---
title: "Airbnb Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)
```

```{r}
airbnb = read_csv("./data/nyc_airbnb.zip") %>% 
  clean_names() %>% 
  rename(boro = neighbourhood_group) %>% 
  mutate(rating = review_scores_location / 2) %>% 
  filter(boro == "Manhattan",
         room_type == "Entire home/apt",
         price > 100 & price < 400)
```
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
airbnb %>% 
  mutate(hover_text = str_c("Price: $", price, '\nRating: ', rating)) %>% #adding text that says price when someone hovers over the points, use /n = new line
  plot_ly(x = ~longitude, y = ~latitude, color = ~price,
          text = ~hover_text,
          type = "scatter", mode = "marker", alpha = 0.5)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood,
          type = "box", colors = "Set2")
```

### Chart C

```{r}
airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, 
          type = "bar")
```

