---
title: "Interactivity"
author: "Ahlam Abuawad"
date: "11/1/2017"
output: html_document
---

### Load Libraries

```{r_load_libraries}
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)
```

## Dataset - cleaned and tidied

```{r}
airbnb = read_csv("./data/nyc_airbnb.zip") %>% 
  clean_names() %>% 
  rename(boro = neighbourhood_group) %>% 
  mutate(rating = review_scores_location / 2) %>% 
  filter(boro == "Manhattan",
         room_type == "Entire home/apt",
         price > 100 & price < 400)
```

## Plotly Scatterplot

```{r}
airbnb %>% 
  mutate(hover_text = str_c("Price: $", price, '\nRating: ', rating)) %>% #adding text that says price when someone hovers over the points, use /n = new line
  plot_ly(x = ~longitude, y = ~latitude, color = ~price,
          text = ~hover_text,
          type = "scatter", mode = "marker", alpha = 0.5)
```

Scatter - can be taken as several plots such as glm, therefore add mode to add markers
Can now interact with plot and zoom in on certain areas, pan, click, drag, etc. 
Plotly plots embed automatically as a gglplot would

## Plotly Boxplot

```{r}
airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood,
          type = "box", colors = "Set2")
```

## Plotly Barchart

```{r}
airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, 
          type = "bar")
```

## ggplotly --> turns ggplot into interactive plot

```{r}
scatter_ggplot = airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.25) +
  scale_color_viridis() +
  coord_cartesian() +
  theme_classic()

ggplotly(scatter_ggplot)
```

not as much hover control as plotly

## ggplotly boxplot

```{r}
box_ggplot = 
  inner_join(airbnb, common_neighborhoods,
             by = "neighbourhood") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price, fill = neighbourhood)) +
  geom_boxplot() +
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplotly(box_ggplot)
```


